\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}

\geometry{margin=2.5cm}

\title{\textbf{USGS 30-Day Seismic Baseline}\\
Contextual Reference for TCDS Hunter TRL-9}
\author{Genaro Carrasco Ozuna\\
Proyecto TCDS}
\date{\today}

\begin{document}
\maketitle

\section*{Purpose of This Document}
This document provides a formal, auditable description of the \textbf{USGS 30-day seismic dataset}
used by the \textbf{TCDS Hunter System} exclusively as a \textit{statistical baseline} for
Zoom-Out analysis.

The dataset is \textbf{not modified, reinterpreted, or redistributed as primary data}.
It is consumed as a reference layer to compute deviations (Z-score) and coherence metrics.

\section*{Data Source}
\begin{itemize}
  \item Provider: United States Geological Survey (USGS)
  \item Product: Earthquake Catalog – Past 30 Days
  \item Endpoint:
  \begin{verbatim}
https://earthquake.usgs.gov/earthquakes/feed/v1.0/summary/2.5_month.geojson
  \end{verbatim}
  \item Retrieval Mode: Automated (read-only)
\end{itemize}

\section*{Role Within TCDS Architecture}
Within the TCDS paradigm, this dataset plays a \textbf{passive, $\phi$-driven role}:

\begin{itemize}
  \item It defines the \textbf{historical expectation} ($\mu$) of regional seismicity.
  \item It enables computation of:
  \[
  Z = \frac{N_{\text{current}} - \mu}{\sigma}
  \]
  \item It does \textbf{not} trigger alerts by itself.
\end{itemize}

Active detection is performed exclusively by:
\begin{itemize}
  \item Entropy collapse ($\Delta H$)
  \item Locking Index (LI)
  \item Causal Time ($t_C$)
  \item E-Veto validation
\end{itemize}

\section*{Separation of Responsibility}
\begin{itemize}
  \item USGS data: \textbf{Observational, external, authoritative}
  \item TCDS Hunter output: \textbf{Derived, causal, internal}
\end{itemize}

This separation guarantees:
\begin{itemize}
  \item No claim of ownership over USGS data
  \item No alteration of original records
  \item Full legal and scientific compliance
\end{itemize}

\section*{Reproducibility and Traceability}
Each ingestion includes:
\begin{itemize}
  \item Retrieval timestamp (UTC)
  \item SHA-256 hash of the raw GeoJSON file
  \item Configuration hash of the Hunter/Crawler run
\end{itemize}

These elements ensure deterministic replay and forensic auditability.

\section*{Licensing Note}
USGS datasets are used under their public data policy.
This document and all TCDS-derived analyses are licensed independently and
do not impose restrictions on the original USGS material.

\section*{Conclusion}
The USGS 30-day dataset functions strictly as a \textbf{contextual baseline}.
All predictive, causal, and operational claims originate solely from
the TCDS Hunter system.

\end{document}

